---
title: "R Notebook"
output: html_notebook
---

# ml_word_visualisations

## Structure of repository

Folder [lda](./lda) consists of the files to run lda experiments 
1. [utils.R](./lda/utils.R) which includes functions for testing lda topics 
2. [main.R](./lda/main.R) which includes methods for creating and testing lda models from different libraries

Folder [data](./data) is there to store your data. <br>
Folder [results](./results) stores the results of your experiment

## Example 

### LDA
#### 0. Preparation
  #### 0.1 Set (hyper)parameters

**Data** 
```{r}
data <- read_csv("./data/depression_anxiety_final_2.csv")
data_col <- "dep_text"
group_var <- NULL # now necessary, but only used for t-test
cor_var <- "PHQtot"
```


**BERTopic**
```{r}
model_type <- "bert_topic" # or "mallet"
data_col <- "dep_text"
embedding_model <- "distilroberta"
umap_model <- "default"
hdbscan_model <- "default"
vectorizer_model <- "default"
representation_model <- "default"
num_top_words <- 10
stop_words = "english"
n_gram_window <- c(1,3)
min_df <- 5
reduce_frequent_words <- TRUE
bm25_weighting <- TRUE
seed=1234
```

**Analysis**
```{r}
cor_var <- "PHQtot" # grouping variable for t-test, to be predicted variable for other
control_vars <- c("PHQtot")#, "GADtot") # vector of variables to control analysis with if test_method is linear_regression
test_method <- "textTrain_regression" # linear_regression, logistic_regression, t-test
```

**Miscellaneous** 
```{r}
seed <- 1234
```

##### 0.2 Create directory to save all computations
All objects created within the pipeline are created in the directory below. These include
- Document Term Matrix
- model
- predictions
- analysis results
```{r}
save_dir <- paste0("./results/",
            model_type,"_",
            data_col, "_",
            "embed_", embedding_model,
            "_min_df_", min_df,
            "_bm25_weighting_", bm25_weighting)#,)
if (!dir.exists("./results")) {
  dir.create("./results")
}
```

##### 0.3 Imports
```{r}
library(textmineR)
library(tidyverse)
library(dplyr)
library(textmineR)
library(mallet)
library(rJava)
library(tokenizers)
library(text2vec)
library(quanteda)
source("./topic_modeling/lda/main.R")
source("./topic_modeling/lda/wordclouds.R")

```


#### 1 Create bert topic model
```{r}
#data <- data.frame(read_csv("./data/suicide_test.csv"))
bertopic <- get_bertopic_model(data=data,
                        data_var="dep_text",
                        embedding_model=embedding_model,
                        umap_model=umap_model,
                        hdbscan_model=hdbscan_model,
                        vectorizer_model=vectorizer_model,
                        representation_model=representation_model,
                        num_top_words=num_top_words,
                        n_gram_range=n_gram_window,
                        min_df=min_df,
                        bm25_weighting=bm25_weighting,
                        reduce_frequent_words=reduce_frequent_words,
                        stop_words=stop_words,
                        save_dir=save_dir)
```

```{r}
data2 <- read_csv("./data/depression_anxiety_final_2.csv")
view(data2)
```


#### 2. Analysis

```{r}

test <- get_lda_test(model=bertopic$model,
                    preds=bertopic$preds,
                    data=bertopic$train_data,
                    group_var = "PHQtot",
                    control_vars = c("PHQtot"),
                    test_method = "textTrain_regression",
                    seed=seed,
                    save_dir=save_dir)
```


```{r}
test <- get_lda_test(model=bertopic$model,
                    preds=bertopic$preds,
                    data= bertopic$train_data,
                    group_var = "PHQtot",
                    control_vars = c("PHQtot"),
                    test_method = "linear_regression",
                    seed=seed,
                    save_dir=save_dir)
view(test)
```

```{r}

plot_wordclouds(model = model,
                model_type = "bert_topic",
                test = test,
                test_type = "linear_regression",
                cor_var = "PHQtot",
                plot_topics_idx = NULL,
                p_threshold = 0.05,
                scale_size=FALSE,
                color_negative_cor = scale_color_gradient(low = "darkgreen", high = "green"),
                color_positive_cor = scale_color_gradient(low = "darkred", high = "red"),
                save_dir=save_dir,
                seed=seed)
```
