---
title: "R Notebook"
output: html_notebook
---

## using LDA model of textmineR
- mallet will be supported later
- data is private therefore not included in repository

```{r}
library(textmineR)
library(tidyverse)
library(dplyr)

model <- readRDS("./results/textmineR_dep_all_words_20_most_1_least_0_frequency_0_pred_function/seed_5/model.rds")
#preds <- readRDS("./results/dep_all_words_100_most_0_least_0_frequency_0.003/seed_5/preds.rds")
data.frame(model$)

```
```{r}
source("./lda/main.R")

library(textmineR)
library(tidyverse)
library(dplyr)

model <- readRDS("./results/mallet_dep_all_words_20_most_1_least_0_frequency_0_pred_function/seed_5/model.rds")
#preds <- readRDS("./results/dep_all_words_100_most_0_least_0_frequency_0.003/seed_5/preds.rds")
#model <- name_cols_phi(model)
#data.frame(model$pred_model$phi)
#gamma <- CalcGamma(phi = model$pred_model$phi, 
                   #theta = model$pred_model$theta)

data.frame(model$pred_model$phi)

```
```{r}
# Assuming 'column_name' is the name of the column you want to check for uniqueness
df <- read_csv("./data/depression_anxiety_cleaned.csv")
df <- df %>% mutate(unique_id = row_number())
is_unique <- !any(duplicated(df$row_number))
write_csv(df,"./data/depression_anxiety_cleaned.csv")
if (is_unique) {
  cat("The column values are unique.\n")
} else {
  cat("The column has duplicates.\n")
}
```

```{r}
source("./lda/main.R")

dtms <- get_dtm(data_dir = "./data/depression_anxiety_cleaned.csv",
                            id_col = "participant_id",
                            data_col = "dep_all_words",
                            group_var = "minidep_diagnose",
                            ngram_window = c(1,2),
                            stopwords = NULL,
                            removalword = "",
                            occ_rate = 0.003,
                            removal_mode = "absolute",
                            removal_rate_most = 0,
                            removal_rate_least = 0,
                            split=1,
                            seed=seed)

```

```{r}
source("./lda/main.R")

term_document_matrix <- get_relative_frequency_term_document(dtms$train_dtm)
topic_term_matrix <- model$phi
view(data.frame(term_document_matrix))
view(data.frame(topic_term_matrix))
length(model$vocabulary)
colnames(topic_term_matrix) <- as.character(unlist(model$vocabulary))
view(term_document_matrix[1,])
```


```{r}
source("./lda/main.R")
term_document_matrix <- get_relative_frequency_term_document(dtms$train_dtm)
topic_document_matrix <- get_topic_per_document_dist(topic_term_matrix = model$phi,
                                                     term_document_matrix = term_document_matrix,
                                                     vocabulary = model$vocabulary)
view(data.frame(topic_document_matrix))

```

```{r}
preds <- readRDS("./")
```{r}
topic_document_matrix <- array(0, dim = c(100, 900))
print(dim(topic_document_matrix))
view(data.frame(topic_document_matrix))
```

```{r}
docs <- Dtm2Docs(dtms$train_dtm)
  
model <- MalletLDA(num.topics = num_topics,
                            alpha.sum = 5,
                            beta = 0.01)
instances <- mallet.import(as.character(seq_along(docs)),
                             docs,
                             #"example_stoplist.csv",
                             preserve.case = FALSE,
                             token.regexp= "[\\p{L}\\p{N}_]+|[\\p{P}]+\ ")

model$loadDocuments(instances)
#instances

```


```{r}
source("./lda/main.R")
dtm2 <- get_dtm_to_df(dtms$train_dtm)
view(dtm2)
```



```{r}
source("./lda/main.R")

num_topics <- c(20)
answer_type <- c("all_words")#,"all_phrases", "text")
categories <- c("dep")#, "wor")
removal_frequencies_most <- c(1)#, 0.0025, 0.005)
removal_frequencies_least <- c(0)#, 0.01, 0.02, 0.03)
removal_mode <- "absolute"
seed <- 5
removal_frequencies <- c(0)#,6,7,8,9,10)
pred_mode <- c("custom")
model_type <- c("mallet")


for (num_topic in num_topics){
  for (type in answer_type){
    for (category in categories){
      for (most in removal_frequencies_most){
        for (least in removal_frequencies_least){
          for (frequency in removal_frequencies){
            for (mode in pred_mode){
              for (model in model_type){
                tryCatch({
                  save_dir <- ""
                  if (category=="dep"){
                    group_var <- "minidep_diagnose"
                  } else {
                    group_var <- "miniGAD_diagnose"
                  }
                  #print(num_topic)
                  #print(type)
                  #print(category)
                  dtms <- get_dtm(data_dir = "./data/depression_anxiety_cleaned.csv",
                                  id_col = "unique_id",
                                  data_col = paste0(category, "_", type),
                                  group_var = group_var,
                                  ngram_window = c(1,3),
                                  stopwords = NULL,
                                  removalword = "",
                                  occ_rate = frequency,
                                  removal_mode = removal_mode,
                                  removal_rate_most = most,
                                  removal_rate_least = least,
                                  split=1,
                                  seed=seed)
            
                  save_dir <- paste0("./results/",model,"_",category, "_", type, "_", num_topic, "_most_",most, "_least_", least, "_frequency_", frequency, "_pred_", mode)
                  #print(save_dir)
                  model <- get_lda_model(model_type=model,
                                         dtm=dtms$train_dtm,
                                         num_topics=num_topic,
                                         num_top_words=10,
                                         num_iterations = 2000,
                                         seed=seed,
                                         save_dir = save_dir)
            
                  preds <- get_lda_preds(model = model,
                                         num_iterations=500,
                                         data = dtms$train_data,
                                         dtm = dtms$train_dtm,
                                         group_var = c(group_var,
                                                     "Gender",
                                                     "age",
                                                     "PHQtot",
                                                     "GADtot"),
                                         seed=seed,
                                         mode=mode,
                                         save_dir = save_dir)
                }, error = function(err) {
                    # Handle the error or do nothing to continue with the loop
                    # You can print an error message, log it, or simply continue the loop
                    cat("An error occurred: ", conditionMessage(err), "\n")
                  }
                )
              }
            }
          }
        }
      }
    }
  }
}
```

```{r}
source("./lda/main.R")

num_topics <- c(20)
answer_type <- c("all_words")#,"all_phrases", "text")
categories <- c("dep")#, "wor")
removal_frequencies_most <- c(1)#, 0.0025, 0.005)
removal_frequencies_least <- c(0)#0.01, 0.02, 0.03, 0.04, 0.05)
removal_frequencies <- c(0)#,6,7,8,9,10)
pred_mode <- c("function")
model_type <- c("mallet")
seed <- 5

for (num_topic in num_topics){
  for (type in answer_type){
    for (category in categories){
      for (most in removal_frequencies_most){
        for (least in removal_frequencies_least){
          for (frequency in removal_frequencies){
            for (mode in pred_mode){
              for (model in model_type){
                tryCatch({
                # Code that may produce an error
                # ...
                  dir <- paste0("./results/", model, "_",category, "_", type, "_", num_topic, "_most_",most, "_least_", least, "_frequency_", frequency,"_pred_", mode, "/seed_", seed)
                  print(dir)
                  model <- readRDS(paste0(dir, "/model.rds"))
                  preds <- readRDS(paste0(dir, "/preds.rds"))
          
                  variable <- c("PHQtot", "GADtot")
                  estimates <- c()
                  t_values <- c()
                  p_values <- c()

                  test <- get_lda_test(model=model,
                                   preds=preds,
                                   group_var = "PHQtot",
                                   control_vars = c("randnumber"),
                                   test_method = "textTrain_regression",
                                   seed=seed)
          
                  estimates <- c(estimates, test$estimate)
                  t_values <- c(t_values, test$statistic)
                  p_values <- c(p_values, test$p.value)

                  test <- get_lda_test(model=model,
                                   preds=preds,
                                   group_var = "GADtot",
                                   control_vars = c("randnumber"),
                                   test_method = "textTrain_regression",
                                   seed=seed)
          
                  estimates <- c(estimates, test$estimate)
                  t_values <- c(t_values, test$statistic)
                  p_values <- c(p_values, test$p.value)

                  df <- list(variable = variable,
                         estimate = estimates,
                         t_value = t_values,
                         p_value = p_values)
                  write_csv(data.frame(df), paste0(dir, "/textTrain_regression.csv"))
                # If the error occurs, it will be caught here
                }, error = function(err) {
                  # Handle the error or do nothing to continue with the loop
                  # You can print an error message, log it, or simply continue the loop
                  cat("An error occurred: ", conditionMessage(err), "\n")
                  }
                )
              }
            }
          }
        }
      }
    }
  }
}

```

```{r}
source("./lda/main.R")

num_topics <- c(20)
answer_type <- c("all_words")#,"all_phrases", "text")
categories <- c("dep")#, "wor")
removal_frequencies_most <- c(1)#, 0.0025, 0.005)
removal_frequencies_least <- c(0)#0.01, 0.02, 0.03, 0.04, 0.05)
removal_frequencies <- c(0)#,6,7,8,9,10)
pred_mode <- c("function")
model_type <- c("mallet")

seed <- 5

variable_column <- c()
estimate_column <- c()
t_value_column <- c()
p_value_column <- c()
num_topic_column <- c()
type_column <- c()
category_column <- c()
removal_most_column <- c()
removal_least_column <- c()
removal_frequency_column <- c()
pred_mode_column <- c()
model_type_column <- c()

for (num_topic in num_topics){
  for (type in answer_type){
    for (category in categories){
      for (most in removal_frequencies_most){
        for (least in removal_frequencies_least){
          for (frequency in removal_frequencies){
            for (mode in pred_mode){
              for (model in model_type){
                tryCatch({
                  dir <- paste0("./results/", model, "_",category, "_", type, "_", num_topic, "_most_",most, "_least_", least, "_frequency_",frequency,"_pred_",mode,"/seed_", seed)
                  test <- read_csv(paste0(dir, "/textTrain_regression.csv"))
                  category_column <- c(category_column, category)
                  type_column <- c(type_column, type)
                  removal_most_column <- c(removal_most_column, most)
                  removal_least_column <- c(removal_least_column, least)
                  removal_frequency_column <- c(removal_frequency_column, frequency)
                  num_topic_column <- c(num_topic_column, num_topic)
                  model_type_column <- c(model_type_column, model)
                  pred_mode_column <- c(pred_mode_column, mode)
                  variable_column <- c(variable_column, test$variable[1])
                  estimate_column <- c(estimate_column, test$estimate[1])
                  t_value_column <- c(t_value_column, test$t_value[1])
                  p_value_column <- c(p_value_column, test$p_value[1])
                  category_column <- c(category_column, category)
                  type_column <- c(type_column, type)
                  num_topic_column <- c(num_topic_column, num_topic)
                  removal_most_column <- c(removal_most_column, most)
                  removal_least_column <- c(removal_least_column, least)
                  removal_frequency_column <- c(removal_frequency_column, frequency)
                  model_type_column <- c(model_type_column, model)
                  pred_mode_column <- c(pred_mode_column, mode)
                  variable_column <- c(variable_column, test$variable[2])
                  estimate_column <- c(estimate_column, test$estimate[2])
                  t_value_column <- c(t_value_column, test$t_value[2])
                  p_value_column <- c(p_value_column, test$p_value[2])
            
                  df <- list(category = category_column,
                             type = type_column,
                             num_topics = num_topic_column,
                             model_type = model_type_column,
                             pred_mode = pred_mode_column,
                             removal_frequency_most = removal_most_column,
                             removal_frequencies_least = removal_least_column,
                             removal_default_frequency = removal_frequency_column,
                             variable = variable_column,
                             estimate = estimate_column,
                             t_value = t_value_column,
                             p_value = p_value_column)
                  write_csv(data.frame(df), paste0("./results/textTrain_regression_all_seed_", seed, "_6.csv"))
                }, error = function(err) {
                    # Handle the error or do nothing to continue with the loop
                    # You can print an error message, log it, or simply continue the loop
                    cat("An error occurred: ", conditionMessage(err), "\n")
                  }
                )
              }
            }
          }
        }
      }
    }
  }
}
```

```{r}
model <- readRDS("./results/textmineR_dep_all_words_20_most_1_least_0_frequency_0_pred_function/seed_5/model.rds")
preds <- readRDS("./results/textmineR_dep_all_words_20_most_1_least_0_frequency_0_pred_function/seed_5/preds.rds")
view(model$summary)
test <- get_lda_test(model=model,
                     preds=preds,
                     group_var = "PHQtot",
                     control_vars = c("PHQtot"),
                     test_method = "linear_regression",
                     seed=5)
view(test)
```

```{r}
model <- readRDS("./results/textmineR_dep_all_words_20_most_1_least_0_frequency_0_pred_function/seed_5/model.rds")
preds <- readRDS("./results/textmineR_dep_all_words_20_most_1_least_0_frequency_0_pred_function/seed_5/preds.rds")
#view(model$summary)
test <- get_lda_test(model=model,
                     preds=preds,
                     group_var = "minidep_diagnose",
                     control_vars = c("PHQtot"),
                     test_method = "t-test",
                     seed=5)
view(test)
```

```{r}
model <- readRDS("./results/dep_all_words_100/seed_2/model.rds")
view(model$summary)
```

```{r}
preds <- readRDS("./results/dep_all_words_20_most_5_least_0_frequency_0/seed_1234/preds.rds")
num_topics <- 100

# rename topic columns
for (i in 1:num_topics) {
  old_column_name <- paste0("t_", i)
  new_column_name <- paste0("Dim", i, "_texts")
      
  if (old_column_name %in% colnames(preds)) {
    colnames(preds)[colnames(preds) == old_column_name] <- new_column_name
  }
}
    
dims <- as.data.frame(preds) %>% select(contains("Dim"))
dims <- as_tibble(dims)
preds <- as_tibble(preds)
for (col in colnames(dims)) {
  dims[[col]] <- as.numeric(dims[[col]])
}

for (i in 1:100){
  plot(x=dims[[paste0("Dim", i, "_texts")]], 
       y=preds$PHQtot, 
       xlabel = paste0("Topic",i))
}
```

```{r}
write_csv(data.frame(df), paste0(dir, "/textTrain_regression.csv"))
```
```{r}
test$p.value[1]

```

```{r}
saveRDS(preds, "./dep_all_words_20/seed_1234/preds.rds")
```

```{r}
preds <- data.frame(readRDS("./dep_all_words_20/seed_1234/preds.rds"))
for (i in 1:20) {
  old_column_name <- paste0("t_", i)
  new_column_name <- paste0("Dim", i, "_texts")
  
  if (old_column_name %in% colnames(preds)) {
    colnames(preds)[colnames(preds) == old_column_name] <- new_column_name
  }
}
```


```{r}
library(text)
library(reticulate)
use_condaenv("text_package", required = TRUE)
dims <- as.data.frame(preds) %>% select(contains("Dim"))
view(dims)
for (col in colnames(dims)) {
  dims[[col]] <- as.numeric(dims[[col]])
}
trained_model <- textTrainRegression(
  x = dims,
  y = preds$PHQtot,
  multi_cores = FALSE # This is FALSE due to CRAN testing and Windows machines.
)

# Examine results (t-value, degree of freedom (df), p-value, alternative-hypothesis,
# confidence interval, correlation coefficient).

trained_model$results

```

