---
title: "R Notebook"
output: html_notebook
---

# ml_word_visualisations

## Structure of repository

Folder [lda](./lda) consists of the files to run lda experiments 
1. [utils.R](./lda/utils.R) which includes functions for testing lda topics 
2. [main.R](./lda/main.R) which includes methods for creating and testing lda models from different libraries

Folder [data](./data) is there to store your data. <br>
Folder [results](./results) stores the results of your experiment

## Example 

### LDA
#### 0. Preparation
#### 0.1 Set (hyper)parameters

**Data** 
```{r}
data_dir  <- "./data/chat_text_survey_liv.csv"
data_col  <- "message"
id_col    <- "caseId"
group_var <- NULL # now necessary, but only used for t-test
cor_var   <- "age_liv_pre"
```

**Document Term Matrix** 
```{r}
swedish_stopword <- stopwords::stopwords("sv",
                                         source = "snowball")
english_stopword <- stopwords::stopwords("en",
                                         source = "snowball")
all_stopword     <- c(swedish_stopword, english_stopword,
                  "t", "ex", "t_ex", "sån", "it", "me", "and", "in", "the",
                  "https", "www", "com", "d", "o", "ör", "aa", "osv",
                  "mm", "https_www", "o", "to", "e", "å", "to", "mm", 
                  "å", "e", "pch", "x", "tja", "lr",
                  "a", "that", "jo", "ja_ja", "ja_jo", "nej_ja", "ja_nej", "hej",
                  "hejj", "hejdå", "näe", "ne", "m", "nä", "f", "n", "im", "crazy", 
                  "jsg", "v", "q",
                  "my", "but", "for", "have", "is", "of", "you", "don", "not", "he",
                  "quot", "dom", "va", "alltså", "ens", "också", "bara",
                  "även", "kommer", "fick", "fast", "även", "nåt", "något",
                  "nog", "kram_övningen", "kram_övning", "ajg", "johan", 
                  "ye", "buyf", "watch_ye", "youtube_watch", "youtube_watch_ye")

ngram_window      <- c(1,3)
stopwords         <- all_stopword
removalword       <- "" # just possible with one word
occ_rate          <- 0.005
removal_num_most  <- 500 #0.01 
removal_num_least <- 0  #0.10
removal_mode      <- "absolute" # relative absolute threshold
split             <- 1
```


**LDA** 
```{r}
model_type     <- "mallet" # "textmineR" or "mallet"
pred_mode      <- "mallet" # "mallet" "function" or "custom" for mallet
num_topics     <- 100
num_top_words  <- 10
num_train_iterations <- 2000
num_pred_iterations  <- 1000
```

**Analysis**
```{r}
cor_var <- "age_liv_pre" # grouping variable for t-test, to be predicted variable for other
control_vars <- c("age_liv_pre") # vector of variables to control analysis with if test_method is linear_regression
test_method <- "textTrain_regression" # linear_regression, logistic_regression, t-test
```

**Miscellaneous** 
```{r}
seed <- 1234
```

##### 0.2 Create directory to save all computations
All objects created within the pipeline are created in the directory below. These include
- Document Term Matrix
- model
- predictions
- analysis results
```{r}
save_dir <- paste0("./results/",
            model_type,"_",
            data_col, "_",
            num_topics, 
            "_most_",removal_num_most, 
            "_least_", removal_num_least, 
            "_occ_", occ_rate, 
            "_pred_", pred_mode)
if (!dir.exists("./results")) {
  dir.create("./results")
}
```

##### 0.3 Imports
```{r}
library(textmineR)
library(tidyverse)
library(dplyr)
library(textmineR)
library(mallet)
library(rJava)
library(tokenizers)
library(text2vec)
library(quanteda)
source("./lda/main.R")
source("./lda/wordclouds.R")
source("./lda/inferencer.R")
```

#### 1. Compute Document Term Matrix
```{r}
dtms <- get_dtm(data_dir = data_dir,
                id_col = id_col,
                data_col = data_col,
                group_var = group_var, # used if t-test, is binary, so this is optional
                cor_var = cor_var, # used for regression, correlation
                ngram_window = ngram_window,
                stopwords = stopwords,
                removalword = removalword,
                occ_rate = occ_rate,
                removal_mode = removal_mode,
                removal_rate_most = removal_num_most,
                removal_rate_least = removal_num_least,
                split=split,
                seed=seed,
                save_dir=save_dir)

length(colSums(dtms$train_dtm))
colSums(dtms$train_dtm)
colSums(dtms$train_dtm)[(length(colSums(dtms$train_dtm)) - 100):length(colSums(dtms$train_dtm))]
# 4813 
# 4247 entries
# 10 %  = 265
# 5%    = 608
# 0.015 = 1751
# 1%    = 2673
# 0.5%  = 5366

```

#### 2. Create LDA Model
```{r}
model <- get_lda_model(model_type = model_type,
                        dtm = dtms$train_dtm,
                        num_topics = num_topics,
                        num_top_words = num_top_words,
                        num_iterations = num_train_iterations,
                        seed = seed,
                        save_dir = save_dir)
View(model$top_terms)
# model$top_terms %>% as_tibble()
```

#### 3. Create Predictions with MALLET
```{r}
inference_model <- model$model$getInferencer()

mallet_instance <- model$instances

preds <- get_lda_preds(
  model = model$model,
  num_iterations = num_pred_iterations,
  data = dtms$train_data,
  dtm = NULL, # NULL because we are using mallet_instance below 
  mallet_instance = mallet_instance,
  group_var = c(cor_var),
  seed = seed,
  mode = pred_mode,
  save_dir = save_dir)

```

#### 4. Reload objects
```{r}


#in./results/textmineR_message_300_most_500_least_0_occ_0.005_pred_function/seed_1234/preds.rds"
d
tms <- readRDS("results/textmineR_message_300_most_25_least_0_occ_0.005_pred_function/seed_1234/dtms.rds")

# model <- readRDS("results/textmineR_message_300_most_500_least_0_occ_0.005_pred_function/seed_1234/model.rds")
model$phi[1]
rownames(model$phi[1])
colnames(model$phi[1])
model$phi[1]
is.matrix(model$phi)
is.data.frame(model$phi)
preds <- readRDS("results/textmineR_message_300_most_25_least_0_occ_0.005_pred_function/seed_1234/preds.rds")

```


#### 4. Analysis
##### 4.1 textTrain_regression
```{r}
test <- get_lda_test(
  model = model,
  data = dtms$train_data,
  preds = preds,
  group_var = cor_var,
  control_vars = control_vars,
  test_method = "textTrain_regression",
  seed = seed,
  save_dir = save_dir)
```


#### POS and NEG
```{r}
test_pos_neg <- get_lda_test(
  model = model,
  data = dtms$train_data,
  preds = preds,
  group_var = cor_var,
  control_vars = control_vars,
  test_method = "linear_regression",
  seed=seed,
  save_dir=save_dir
  )
View(test_pos_neg)
```

```{r}

plot_wordclouds(model = model,
                test = test_pos_neg,
                test_type = "linear_regression",
                cor_var = "age_liv_pre",
               # plot_topics_idx = c(4, 8, 10, 37, 55, 57, 60, 89), # Diagnos
               # plot_topics_idx = c(2, 15, 24, 25, 29, 48, 68, 75, 76, 83), # Suicide
              #  plot_topics_idx = c(28, 29, 31, 38, 51, 56, 58, 59, 61), # Känslor
              #  plot_topics_idx = c(23, 32, 82, 34, 50, 49, 19, 64, 65, 13), # Värld, Vård, HBV
              #  plot_topics_idx = c(11, 12, 14, 22, 40, 49, 94), #Skola, alkohol, övergrepp
                plot_topics_idx = c(92,96), # Positiv
                p_threshold = NULL,
                color_negative_cor = scale_color_gradient(
                  low = "darkgray", high = "black"),
                color_positive_cor = scale_color_gradient(
                  low = "darkgray", high = "black"),
                save_dir=save_dir,
                seed=seed)
```




##### 4.2 AGE
```{r}
test_age <- get_lda_test(
  model = model,
  data = dtms$train_data,
  preds = preds,
  group_var = cor_var,
  control_vars = control_vars,
  test_method = "linear_regression",
  seed=seed,
  save_dir=save_dir
  )
mean(dtms$train_data$age_liv_pre, na.rm=T)
range(dtms$train_data$age_liv_pre, na.rm=T)
table(is.na(dtms$train_data$age_liv_pre))
View(test_age)
```

```{r}

plot_wordclouds(model = model,
                test = test_age,
                test_type = "linear_regression",
                cor_var = "age_liv_pre",
                plot_topics_idx = NULL,
                p_threshold = 0.05,
                color_negative_cor = scale_color_gradient(
                  low = "blue", high = "darkblue"),
                color_positive_cor = scale_color_gradient(
                  low = "purple", high = "#36013F"),
                save_dir=save_dir,
                seed=seed)
```






##### 4.2 Gender
```{r}
dtms$train_data$Gender <- dtms$train_data$gender_liv_pre

dtms$train_data$Gender[dtms$train_data$Gender == "Flicka/kvinna"] <- 1
dtms$train_data$Gender[dtms$train_data$Gender == "Pojke/man"] <- 2

dtms$train_data$Gender <- as.numeric(dtms$train_data$Gender)

test_gender <- get_lda_test(model=model,
                     data = dtms$train_data,
                    preds=preds,
                    group_var = "Gender",
                    control_vars = "Gender",
                    test_method = "linear_regression",
                    seed=seed,
                    save_dir=save_dir)
View(test_gender)
```
```{r}

plot_wordclouds(model = model,
                test = test_gender,
                test_type = "linear_regression",
                cor_var = "Gender",
                plot_topics_idx = NULL,
                p_threshold = 0.05,
                color_negative_cor = scale_color_gradient(
                  low = "darkgray", high = "purple"),
                color_positive_cor = scale_color_gradient(
                  low = "darkgray", high = "darkblue" ),
                save_dir = save_dir,
                seed = seed)
```

##### 4.2 Duration of chat
```{r}

test_duration <- get_lda_test(
  model = model,
  data = dtms$train_data,
  preds = preds,
  group_var = "durationMinutesNoOutlier",
  control_vars = c("durationMinutesNoOutlier"),
  test_method = "linear_regression",
  seed = seed,
  save_dir = save_dir
  )
View(test_duration)
```
```{r}

plot_wordclouds(model = model,
                test = test_duration,
                test_type = "linear_regression",
                cor_var = "durationMinutesNoOutlier",
                plot_topics_idx = NULL,
                p_threshold = 0.05,
                color_negative_cor = scale_color_gradient(
                  low = "darkgray", high = "darkgreen"),
                color_positive_cor = scale_color_gradient(
                  low = "darkgray", high = "darkred" ),
                save_dir = save_dir,
                seed = seed)
```


##### 4.2 Hour of day
```{r}
dtms$train_data$Hour <- hour(dtms$train_data$dateTime...4)
dtms$train_data$Hour_cat <- ifelse(
  dtms$train_data$Hour < 7 | 22 < dtms$train_data$Hour,
  1, 2)
dtms$train_data
test_night <- get_lda_test(
  model = model,
  data = dtms$train_data,
  preds = preds,
  group_var = "Hour_cat",
  control_vars = "Hour_cat",
  test_method = "linear_regression",
  seed = seed,
  save_dir = save_dir)
table(dtms$train_data$Hour_cat)
View(test_night)
```



```{r}

plot_wordclouds(model = model,
                test = test_night,
                test_type = "linear_regression",
                cor_var = "Hour_cat",
                plot_topics_idx = NULL,
                p_threshold = 0.05,
                color_negative_cor = scale_color_gradient(
                  low = "darkgray", high = "darkred"),
                color_positive_cor = scale_color_gradient(
                  low = "darkgray", high = "darkgreen"),
                save_dir = save_dir,
                seed = seed)
```















